Computing astrophysical inferences with diffusive nested sampling

### 2014-02-23 ms.tex
Minor edits

Computing the consequences of a posterior distribution can be a challenging
task. Usually we want to marginalise out nuisance parameters, to compute
particular posterior probabilities such as $P(\theta > 1.5)$, or to summarise
the posterior distribution for easy communication with others.
Markov Chain Monte Carlo (MCMC) algorithms provide a general set of tools
for achieving these goals. However, many standard MCMC algorithms are not
capable of exploring complicated probability distributions in a reasonable time.
Problems often occur due to multimodality, strong dependencies, and phase
transitions.

\section{Nested sampling}
The key idea of Nested Sampling \citep{skilling} is that Bayesian computation
should start from the prior $\pi(\pars)$ and move through a sequence of
distributions that successively compress the prior volume by a constant factor
that is (approximately) known.

>>>>

Computing the consequences of a posterior distribution can be a challenging
task. Usually we want to marginalise out nuisance parameters, to compute
particular posterior probabilities such as $P(\theta > 1.5)$, or to summarise
the posterior distribution for easy communication with others.
Markov Chain Monte Carlo (MCMC) algorithms provide a general set of tools
for achieving these goals. However, many standard MCMC algorithms are not
capable of exploring complicated probability distributions in a reasonable time.
Problems often occur due to multimodality, strong dependencies, and phase
transitions. Many different solutions have been suggested for overcoming these
challenges. In this paper we will focus on Nested Sampling \citep{skilling}.

\section{Nested sampling}
The key idea of Nested Sampling \citep{skilling} is that Bayesian computation
should begin from the prior $\pi(\pars)$ and move through a sequence of
distributions that successively compress the prior volume by a constant factor
that is (approximately) known.
